``Interestingness'' in Mathematical Theory Exploration

### 2019-12-02 PhDThesis/benchmark.tex
A bunch of cleanup
Fix diagram spacing

\iffalse TODO: Alison: Each chapter should have a description at the start (see
bucketing ``in this chapter'') \fi

@@

  \centering
  \begin{tikzpicture}[node distance=1cm]

@@

    % Preparation
    \draw
      let \p{thm} = (thm.east),
          \p{in}  = (in.north),
          \p{rec} = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=0.5cm]
       (\x{rec}, \y{in}) -- (\x{rec}, \y{thm})
         node [black, midway, right, xshift=0.3cm]
              {Preparation $\S$\ref{section:prep}};

    % Sampling
    \draw
      let \p{thm} = (thm.east),
          \p{gt}  = (sthm.east),
          \p{rec} = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=0.5cm]
       (\x{rec}, \y{thm}) -- (\x{rec}, \y{gt})
         node [black, midway, right, xshift=0.3cm]
              {Sampling $\S$\ref{section:sampling}};

    % Evaluation
    \draw
      let \p{sthm} = (sthm.east),
          \p{rec}  = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=0.5cm]
       (\x{rec}, \y{sthm}) -- (\x{rec}, \y{rec})
         node [black, midway, right, xshift=0.3cm]
              {Evaluation $\S$\ref{section:evaluation}};

  \end{tikzpicture}
  \caption[]{High-level view of the benchmarking methodology described in
    $\S$\ref{sec:benchmark}, showing
    \begin{tikzpicture}
      \node [rectangle, text centered, draw=black]{processes};
    \end{tikzpicture},
    \begin{tikzpicture}
      \node [rectangle, rounded corners, text centered, draw=black]{data};
    \end{tikzpicture} and
    \begin{tikzpicture}
      \node [trapezium, trapezium left angle=70, trapezium right angle=110,
             text centered, draw=black]{inputs};
  \end{tikzpicture}}
  \label{fig:flow_chart}
\end{figure}

>>>>

@@

  \centering
  \scalebox{0.8}{\begin{tikzpicture}[node distance=1cm]

@@

    % Preparation
    \draw
      let \p{thm} = (thm.east),
          \p{in}  = (in.north),
          \p{rec} = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=1.3cm]
       (\x{rec}, \y{in}) -- (\x{rec}, \y{thm})
         node [black, midway, right, xshift=0.5cm]
              {Preparation $\S$\ref{section:prep}};

    % Sampling
    \draw
      let \p{thm} = (thm.east),
          \p{gt}  = (sthm.east),
          \p{rec} = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=1.3cm]
       (\x{rec}, \y{thm}) -- (\x{rec}, \y{gt})
         node [black, midway, right, xshift=0.5cm]
              {Sampling $\S$\ref{section:sampling}};

    % Evaluation
    \draw
      let \p{sthm} = (sthm.east),
          \p{rec}  = (rec.south east)
       in [decorate,decoration={brace, amplitude=10pt}, xshift=1.3cm]
       (\x{rec}, \y{sthm}) -- (\x{rec}, \y{rec})
         node [black, midway, right, xshift=0.5cm]
              {Evaluation $\S$\ref{section:evaluation}};

  \end{tikzpicture}}
  \caption[]{High-level view of the benchmarking methodology described in
    $\S$\ref{sec:benchmark}, showing
    \begin{tikzpicture}
      \node [rectangle, text centered, draw=black]{processes};
    \end{tikzpicture},
    \begin{tikzpicture}
      \node [rectangle, rounded corners, text centered, draw=black]{data};
    \end{tikzpicture} and
    \begin{tikzpicture}
      \node [trapezium, trapezium left angle=70, trapezium right angle=110,
             text centered, draw=black]{inputs};
  \end{tikzpicture}}
  \label{fig:flow_chart}
\end{figure}
